%SECTION: SETUP 
% region: document class 
\documentclass[hidelinks, nonatbib]{elsarticle}
\makeatletter
\let\c@author\relax
\makeatother

% endregion

% region: packages 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{float}
\usepackage{tabularray}
\usepackage{enumitem}
\setlist[enumerate]{label*=\arabic*.}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{hyperref}

% endregion

% region: source files 
% theorems
\input{theorems.tex}

% equations
\input{equations.tex}

% figures
\input{figures.tex}

% tables
\input{tables.tex}

% references
\addbibresource{references.bib}

% endregion

% region: display breaks 
\allowdisplaybreaks

% endregion

% region: title 
\title{
    The Employability Theorem
}
\author{Cao Bittencourt}
\affiliation{{B. Sc. in Economics from EPGE (FGV), RJ, Brazil.}}
\affiliation{{Statistician at Atlas Career Guide Inc., FL, USA.}}
\date{\today}

% endregion

%SECTION: PAPER 
\begin{document}

% region: abstract 
\begin{abstract}
    In this document, the Employability Theorem is demonstrated from a set of fairly tautological axioms, which are presupposed in quantitative career choice and career development methods.
\end{abstract}

\begin{keyword}
    Employability theorem; 
    Career choice; 
    Career development; 
    Vocational choice; 
    Occupational Information Network; 
    O*NET.
\end{keyword}

% endregion

% region: title 
\maketitle

% endregion

% region: contents 
\tableofcontents

% endregion

% region: introduction 
\newpage
\section{Introduction}

% endregion

% region: presuppositions 
\newpage
\section{The Issue of Occupational Complexity}
% In \textcite{intro_match, intro_eq, intro_gene_comp} we defined statistical models to calculate career compatibility, skill set generality, skill set competence, as well as attribute equivalence, and scaled similarity (or interchangeability). All these metrics helped us match individuals to occupations, compare occupations with one another, characterize skill sets, and evaluate their most important attributes.

% When we speak of ``employability'', however, it is clear the above constructs, though implied in the concept of employability in some way, are not, by themselves, proper metrics to quantify it. For indeed, the employability of a person is the percentage of jobs for which they could be hired in a particular subset of the labor market. So, whatever employability happens to be mathematically, it is, of course, proportional to occupational similarity, competence, and interchangeability, as these are all implicit in the ``hireability'' part of the definition. Nevertheless, we also know that employability is its own construct, which fails to be encapsulated by other constructs. We cannot, for instance, simply infer that if a person $k$ has $s_{kq} \in [0,1]$ similarity with occupation $q$ they are, therefore, hireable in precisely $s_{kq}$ percent of that occupation's job posts, even though the real percentage will be proportional to this similarity. And, likewise, competence coefficients $c_k$ and $c_q \in [0,1]$ are not objectively interpretable in terms of hireability, though, again, they seem to part of the equation. The economic processes that determine employability are just too complicated to be described by any of these metrics alone. And the reason for this is that occupations are not fundamentally reducible to a sum of their attributes: in other words, they are \textit{complex}. Thus, to measure employability we must address the issue of occupational complexity and deduce new coefficients from a coherent theoretical framework of careers.

Now, because this series of articles has been of a more applied nature, so far, we did not have a need to expound upon our most basic assumptions. This is not a problem, for these are all quite reasonable, even tautological. However, to demonstrate the Employability Theorem, it is useful to make at least one these assumptions more explicit, as a valuable intuition towards the Theorem follows directly from a simple definition. Of course, we do not need to define things this way, as this first ``stepping stone'' is not actually used in the demonstration itself. [But, being a reasonable and insightful assumption, which can help us understand the issue of occupational complexity and, therefore, of employability, ]. To minimize digressions, the fundamental axioms behind this definition were moved to the Appendix (for these, again, are practically tautological). With this said, we proceed to our definition.

\SklTasks
\SklDifficulty
\SSL
\ComplexTask
\SCL
\ORA
\OCA
``[\dots] the whole is something besides the parts''
Aristotle 980a Metaphysics, Translated by W. D. Ross 

``[\dots] the whole is not the same as the sum of its parts''
Aristotle 100a, Topics, Translated by W. D. Ross
\OCL

\section{Labor Market Conditions and Employer Behavior}
\RA
\HA
% \OEL
% \LMCA

\section{Task Difficulty and Time Allocation}
\TDA

% endregion

% region: demonstration 
\section{The Employability Theorem}
\subsection{Demonstration}
\ET

\subsection{Corollaries}
\PCC

\AEC

\OCC

\ACC

% endregion

% region: implementation 
\section{Example Implementation}
\subsection{Functional Specifications}
\subsection{Occupational Information Network Data}
\subsection{Results}

% endregion

% region: discussion 
\section{Discussion}

% endregion

% region: conclusion 
\section{Conclusion}
[In this paper, we demonstrated the Employability Theorem, and its corollaries. We also proposed a few functional specifications and analyzed the employability and competitiveness planes which they determine. In the next article, we shall implement these methods with real data from the Occupational Information Network.]

% endregion

% region: references 
\newpage
\printbibliography[
    heading=bibintoc,
    title={References}
]

% endregion

% region: appendix 
\newpage
\section*{Appendix A -- Basic Definitions}
\addcontentsline{toc}{section}{Appendix A -- Basic Definitions}

\section*{Appendix B -- Employability and Competitiveness Statistics}
\addcontentsline{toc}{section}{Appendix B -- Employability and Competitiveness Statistics}

% endregion

\end{document}